---
title: "Rtest-2"
author: "Your Name"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(ggplot2)
##Data Reading
df.data <- read.csv("IrisDataset.csv")

# since our target variable "Species" is categorical variable
# first lets convert it to the right data type

df.data$Species <- as.factor(df.data$Species)
  
ggplot(data=df.data,mapping=aes(x = PetalLengthCm, y = PetalWidthCm,color=Species))+
  xlab(" Petal Length (cm)") +
  ylab(" Petal Width (cm)")  +
  ggtitle("Petal Length vs Petal Width grouped by Species")+
  geom_point()
```


# Explanation

## The Scatter point chart above displays 2 variables  found in Iris dataset. The variables are Petal Length and Petal Width. These variables have been used to classify type of species of a flower. Since Species is the target variable, it contains 3 different classes representing 3 different species of flower which are: Iris-setosa, Iris-versicolor and Iris-virginica types.


# Conclusion 

## Using the graph generated above it is evident that Petal Length and Petal Width  variables clearly separates Iris-Setora from the other two species.

## Thus, we can say that Iris-setosa is linearly separable from the other two species(Iris versicolor and Iris virginica) and that there is an overlap between Iris versicolor and Iris virginica.



```{r}
library(ggplot2)
  
ggplot(data=df.data,mapping=aes(x = SepalLengthCm, y = SepalWidthCm,color=Species))+
  xlab(" Sepal Length (cm)") +
  ylab(" Sepal Width (cm)")  +
  ggtitle("Sepal Length vs Sepal Width grouped by Species")+
  geom_point()
```


# Explanation

## The Scatter point chart above displays the other 2 variables in Iris dataset. The variables are Sepal Length and Sepal Width. These variables have been used to classify type of species of a flower. Since Species is the target variable, it contains 3 different classes representing 3 different species of flower which are: Iris-setosa, Iris-versicolor and Iris-virginica types.


# Conclusion 

## Using the graph generated above it is evident that we cannot clearly separate Iris-Setora from the other two species since at least one type of setosa will still overlap with virginica and versicolor type

## Thus, we can say that Iris-setosa is not linearly separable from the other two species(Iris versicolor and Iris virginica) and that there is an overlap among the three types of species.








