---
title: "Rtest-1"
author: "Scatter Point Chart"
date: "`r Sys.Date()`"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(ggplot2)
##Data Reading
iris.df <- read.csv("Iris.csv")

# we have to change our target variable to factor type for it to work
iris.df$Species <- as.factor(iris.df$Species)
  
plt <- ggplot(data = iris.df, mapping = aes(x = PetalLengthCm, y = PetalWidthCm)) 

plt <- plt + geom_point(alpha = 0.7, size = 6, aes(fill = factor(Species)), colour = 'purple', pch = 21)

plt <- plt + labs(title = "Petal Length Vs Width" ,x = "Petal LengthCm", y = "Petal Width Cm")
plt <- plt + theme_minimal()

plt

```
# Explanation

## Above is the Scatter point chart showing 2 out of 4 variables found in Iris dataset. In this case, Petal Length and Petal Width are the variables used. These variables are used as a way of classifying our target variable knows as "Species". The chart will be showing: Iris-setosa, Iris-versicolor and Iris-virginica types.


# Conclusion 

## From the graph We can conclude that, using Petal Length and Petal Width  variables we can accurately separate Iris-Setora from the other two species clearly.

## With this regard, Iris-setosa is linearly separable from the other two species(Iris versicolor and Iris virginica) and that there is an overlap between Iris versicolor and Iris virginica.










